Notes on generating initial models for mapping into {\tt MAESTRO}

### 2010-05-31 docs/initial_models/initial_models.tex
added a suggestion

@@

We begin with raw data, $\rho^{\raw}, T^{\raw}, p^{\raw}$, and
$X^{\raw}$.  Here is the raw data file for each test problem:
\begin{eqnarray}
{\tt test2} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \nonumber \\
{\tt test\_convect} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt initial\_models/kepler/model\_6.e8.raw} \nonumber \\
{\tt spherical\_heat} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \\
{\tt xrb} & \rightarrow & {\tt initial\_models/xrb/sorted\_xrb.raw} \nonumber
\end{eqnarray}
Using the raw data, we need to generate model data with the same
resolution as the base state.  Note that for spherical problems we set
$\Delta r = \Delta x/\mathtt{drdxfac}$.  We use a fortran subroutine
to interpolate the raw data, yielding the model data, $\rho^{\model},
T^{\model}, p^{\model}$, and $X^{\model}$.  The fortran subroutine
then uses an iterative procedure to modify the model data so that it
is thermodynamically consistent with the {\tt MAESTRO} equation of
state (EOS), and also satisfies our chosen hydrostatic equilibrium
(HSE) discretization,
\begin{equation}
\frac{p_r - p_{r-1}}{\Delta r} = \frac{\rho_r + \rho_{r-1}}{2}g,\label{HSE Discretization}
\end{equation}
to a user defined tolerance.  Here are the fortran subroutines for each test problem:
\begin{eqnarray}
{\tt test2} & \rightarrow & {\tt initial\_models/test2/init\_1d.f90} \nonumber \\
{\tt test\_convect} & \rightarrow & {\tt initial\_models/test2/init\_1d.f90} \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt initial\_models/kepler/init\_1d.f90} \nonumber \\
{\tt spherical\_heat} & \rightarrow & {\tt initial\_models/spherical/init\_1d.f90} \nonumber \\
{\tt xrb} & \rightarrow & {\tt initial\_models/xrb/init\_1d.f90} \nonumber
\end{eqnarray}
The model data is not generated at run-time - it must be generated in
advance of running any MAESTRO examples.  The inputs file should point
to the file containing the model data.

>>>>

\MarginPar{I think it would be a good idea to mention some where in here that MAESTRO outputs info that's useful to check --dr of base state and dr of the input file, which should be the same at the finest level; and Maximum HSE Error, which should be some small number.}

@@

MAESTRO needs to be given model data with the same resolution as the base state.
(Note that for spherical problems we set 
$\Delta r = \Delta x/\mathtt{drdxfac}$.)  
We need to generate this from the raw data,
 $\rho^{\raw}, T^{\raw}, p^{\raw}$, and
$X^{\raw}$.  Here is the raw data file for each test problem:
\begin{eqnarray}
{\tt test2} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \nonumber \\
{\tt test\_convect} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt initial\_models/kepler/model\_6.e8.raw} \nonumber \\
{\tt spherical\_heat} & \rightarrow & \mathrm{none-it~ is~ generated~ analytically} \nonumber \\
{\tt xrb} & \rightarrow & {\tt initial\_models/xrb/sorted\_xrb.raw} \nonumber
\end{eqnarray}

We use a fortran subroutine
to interpolate the raw data, yielding the model data, $\rho^{\model},
T^{\model}, p^{\model}$, and $X^{\model}$.  The fortran subroutine
then uses an iterative procedure to modify the model data so that it
is thermodynamically consistent with the {\tt MAESTRO} equation of
state (EOS), and also satisfies our chosen hydrostatic equilibrium
(HSE) discretization,
\begin{equation}
\frac{p_r - p_{r-1}}{\Delta r} = \frac{\rho_r + \rho_{r-1}}{2}g,\label{HSE Discretization}
\end{equation}
to a user defined tolerance.  Here are the fortran subroutines for each test problem:
\begin{eqnarray}
{\tt test2} & \rightarrow & {\tt initial\_models/test2/init\_1d.f90} \nonumber \\
{\tt test\_convect} & \rightarrow & {\tt initial\_models/test2/init\_1d.f90} \nonumber \\
{\tt wdconvect} & \rightarrow & {\tt initial\_models/kepler/init\_1d.f90} \nonumber \\
{\tt spherical\_heat} & \rightarrow & {\tt initial\_models/spherical/init\_1d.f90} \nonumber \\
{\tt xrb} & \rightarrow & {\tt initial\_models/xrb/init\_1d.f90} \nonumber
\end{eqnarray}
The model data is not generated at run-time - it must be generated in
advance of running any MAESTRO examples.  The inputs file should point
to the file containing the model data.

During runtime, MAESTRO will outout information about the Check that ``dr of MAESTRO base state'' and ``dr of input file data''
